Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-05 paper.tex
Respond to reviewer wrt equality constraints.
Respond to reviewer wrt uniform sampling.

The problem solved here differs from classic approaches in two ways:
\begin{enumerate}
\item the set of valid configurations is defined implicitly, as the
  set of collision-free configurations satisfying a given set of
  inverse kinematics balance constraints;
\item the goal submanifold $\goalmanifold$ is also defined implicitly,
  by additional inverse kinematics constraints.
\end{enumerate}
During global planning, we will consider several types of
tasks and constraints for various reasons:
\begin{itemize}
\item Static balance: the CoM of the robot stays above
  the support polygon center, the two feet have fixed position and
  orientation.
\item End-effector position and orientation: the goals of some problems presented
  in the experimental section of this paper are defined as a specific robot hand pose,
  or a gaze direction.
\item Configuration task: our adaptation of randomized motion planning algorithms 
  uses tasks defined as the distance towards a given configuration in $\mathcal{C}$. 
  This will be detailed in the following section.
\end{itemize}

@@

\textbf{We have run this set of motion planning problems 20 times;
  results are compiled in Table~\ref{table:reaching}. We have also
  measured the performance of \texttt{constraint-solver} (Algorithm
  \ref{algo:newton}) when used to project configurations on
  $\manifold$; the average number of iterations is 6.5 per call, and
  the success rate, i.e. the ratio of the number of successfully
  projected configurations over the total number of calls, is above 95
  percent.}

>>>>

The problem solved here differs from classic approaches in two ways:
\begin{enumerate}
\item the set of valid configurations is defined implicitly, as the
  set of collision-free configurations satisfying a given set of
  inverse kinematics balance constraints;
\item the goal submanifold $\goalmanifold$ is also defined implicitly,
  by additional inverse kinematics constraints.
\end{enumerate}
\textbf{During global planning, we will consider several types of
equality constraints for various reasons:}
\begin{itemize}
\item Static balance: the CoM of the robot stays above
  the support polygon center, the two feet have fixed position and
  orientation.
\item End-effector position and orientation: the goals of some problems presented
  in the experimental section of this paper are defined as a specific robot hand pose,
  or a gaze direction.
\item Configuration task: our adaptation of randomized motion planning algorithms 
  uses tasks defined as the distance towards a given configuration in $\mathcal{C}$. 
  This will be detailed in the following section.
\end{itemize}

@@

\textbf{We have run this set of motion planning problems 20 times;
  results are compiled in Table~\ref{table:reaching}. We have also
  measured the performance of \texttt{constraint-solver} (Algorithm
  \ref{algo:newton}) when used to project configurations on
  $\manifold$; the average number of iterations is 6.5 per call, and
  the success rate, i.e. the ratio of the number of successfully
  projected configurations over the total number of calls, is above 95
  percent. This success rate, high as it is, could be further improved
  by sampling a better initial configuration of $\mathcal{C}$, for
  example by introducing a heuristic bias towards statically balanced
  configurations. Nevertheless we choose to sample $\mathcal{C}$
  uniformly-randomly for the sake of genericity.}
